Hydras \& Co.

### 2024-01-29 doc/epsilon0-chapter.tex
Corrections in doc (#177)
* minor change

* small changes in doc

In the rest of this section, we define an inductive type for representing in \texttt{Coq}
all the ordinals strictly  less than  \(\epsilon_0\), then extend some arithmetic operations
to this type, and finally prove that our representation fits well with 
the expected mathematical properties: the order we define is a well order, 
and the decomposition into Cantor normal form  is consistent 
with other usual definitions of ordinals, for instance in \gaia~\cite{Gaia}, Schütte's book~\cite{schutte}, or larger ordinal notations cf. Chapter~\vref{chap:gamma0}.

\paragraph*{Remark}
\label{sec:orgheadline65}
Unless explicitly mentioned, the term ``ordinal" will be used instead of
``ordinal strictly less than \(\epsilon_0\)" (except in Chapter~\ref{chap:schutte} where it stands for ``countable ordinal'', and Chapter~\ref{chap:gamma0}.).

>>>>

In the rest of this section, we define an inductive type for representing in \texttt{Coq}
all the ordinals strictly  less than  \(\epsilon_0\), then extend some arithmetic operations
to this type, and finally prove that our representation fits well with 
the expected mathematical properties: the order we define is a well order, 
and the decomposition into Cantor normal form  is consistent 
with usual definition of ordinals, for instance in \gaia~\cite{Gaia}, Schütte's book~\cite{schutte}, or larger ordinal notations~\vref{chap:gamma0}.

\paragraph*{Remark}
\label{sec:orgheadline65}
Unless explicitly mentioned, the term ``ordinal" will be used instead of
``ordinal strictly less than \(\epsilon_0\)" (except in Chapter~\ref{chap:schutte} where it stands for ``countable ordinal'').
